Deep Reinforcement Learning for Conservation Decisions

### 2020-12-08 manuscript/manuscript.Rmd
comparison to known solution

@@

# train an agent (model) on one of the environments:
env <- gym$make("fishing-v1")
a2c <- sb3$A2C('MlpPolicy', env, verbose=0L, seed = 42L) # Must use L for integers!
a2c$learn(total_timesteps=300000L)
sims <- env$simulate(a2c, reps = 500L)
```

```{r}
fig_fish_sims <- sims %>% 
  filter(rep < 50) %>%
  ggplot(aes(time, state, group = as.factor(rep))) + geom_line(alpha=0.1)
policy <- env$policyfn(a2c, reps = 50L)
fig_fish_policy <- policy %>% ggplot(aes(state, state - action, group=rep)) + geom_point()
```

```{r fig1, fig.cap=""}
fig_fish_sims + fig_fish_policy
```

>>>>

np <- import("numpy")
np.random.seed(24L)

@@

## initialize the environment
env <- gym$make("fishing-v1")
```

```{r eval=!file.exists("cache/a2c.zip")}
# train an agent (model) on one of the environments:
a2c <- sb3$A2C('MlpPolicy', env, verbose=0L, seed = 42L) # Must use L for integers!
a2c$learn(total_timesteps=300000L)
a2c$save("cache/a2c")
```

```{r}
# Simulate management under the trained agent
a2c <- sb3$A2C$load("cache/a2c")
sims <- env$simulate(a2c, reps = 500L)

policy <- env$policyfn(a2c, reps = 50L)
```

```{r}
# Simulate under the optimal solution (given the model)
opt <- gym_fishing$models$escapement(env)
opt_sims <- env$simulate(opt, reps = 500L)
opt_policy <- env$policyfn(opt) %>% rename(optimal = action)

sims_df <- bind_rows(sims, opt_sims, .id = "model")
policy <- left_join(policy, opt_policy)
```

```{r}
ymin <- function(x) last(x[(ntile(x, 20)==1)])
ymax <- function(x) last(x[(ntile(x, 20)==19)])

fig_sims <- 
sims_df %>% 
  group_by(time, model) %>% 
  summarise(ymin = ymin(state),
            ymax = ymax(state),
            state = mean(state), .groups = "drop") %>%
  ggplot(aes(time, state, ymin = ymin, ymax = ymax, fill=model)) + 
  geom_ribbon(alpha= 0.3) + geom_line(aes(col = model))
```

```{r}
fig_policy <- 
  policy %>% ggplot(aes(state, state - action, group=rep)) + 
  geom_point(alpha=.05) + geom_line(aes(y = state - optimal), col = "blue") + 
  coord_cartesian(xlim = c(0, 1.5), ylim=c(0,0.9))
```

```{r fig1, fig.cap=""}
fig_sims + fig_policy
```
